\textbf{CMCS 818J Project Final Report} \\ Implementing Streaming Authenticated Data Structures

### 2012-12-20 doc/final_report/draft_report.tex
Edits to Abstract

\title{\textbf{CMCS 818J Project Final Report}}
\author{Behzad Koosha, Christopher Imbriano}

@@

	While Infrastructure and Platform -as-a-Service products provide clients access to large amounts of computing power and storage capacity, the client must trust the provider with their computation.
	It may be the case that verifying the computation requires too much resources and is infeasible for the client.
	In this report we will discuss a streaming setting in which a client and provider both witness a stream of data.
	In this setting the client is assumed to have limited resources in both storage and computational power, and as such, relies on the provider to serve as a database of sorts from which the client can query about the data stream.

	Papamanthou and Shi \cite{sads} proposed a scheme called Streaming Authenticated Data Structures, which allows the client to verify the provider answers his or her query correctly and does not tamper with the query results.
	The scheme has been shown to be secure and efficient requiring no communication between the client and the provider during the streaming setting.
	The goal of this project is twofold. First, we will be implementing an example of this data
	structure and second, we will be building an application using the SADS primitive.

@@

	In the verifiable computation (VC) problem, a client wishes to compute a complex function f on an input x.
	The client does not trust the server and therefore, would like to be able to verify the correctness of the computation without having to perform the entire computation themselves.
	The increasing use of distributed computing over the internet also makes commoditizes powerful servers.
	The growth of outsourcing computation in the form of cloud computing has attracted a renewed interest in the VC problem, and a considerable amount of research has been devoted to these problems \cite{evsc}.

	The introduced scheme, Streaming Authenticated Data Structure (SADS), does not require any interaction between the client and the server while the stream is observed.
	Three important properties are obtained using this scheme :
	\begin{enumerate}[a.]
		\item Independence of prover (server) and verifier(client) : the prover and the verifier update their internal state without interaction.
		\item Efficiency : It can be shown that an exponential improvement for many commonly queries in the prover's running time can be achieved.
		\item Expressiveness : a wide range of queries such as membership/ non-membership, successor, range search and frequencies can be supported using this scheme.
	\end{enumerate} 
	The ultimate goal of the proposed scheme is to implement the SADS scheme that enable the verification of computation performed by an untrusted resource.

>>>>

\title{\textbf{CMCS 818J Project Final Report} \\ Implementing Streaming Authenticated Data Structures}
\author{Behzad Koosha, Christopher Imbriano}

@@

	While Infrastructure and Platform -as-a-Service products provide clients access to large amounts of computing power and storage capacity, the client must trust the provider with their computation.
	It may be the case that verifying, by replication of the computation, requires too many resources and is infeasible for the client.
	In this report we will discuss a scheme for computation verification in a streaming setting; that is, one in which a client and provider both witness a stream of data.
	In this setting the client is assumed to have limited resources in both storage and computational power, and must rely on the provider to serve as a database of sorts from which the client can query about the data stream.

	Shi and Papamanthou \cite{sads} proposed a scheme called Streaming Authenticated Data Structures which allows a client to verify the correctness and completeness of answers to queries given by an untrusted party.
	The scheme has been shown to be secure and efficient requiring no communication between the client and the provider during the streaming setting.
	The goal of this project is twofold: first, produce this data structure as a library primitive and second produce an application demonstrating the library.
	So far we have implemented this type of data structure as a Ruby library and written a script to demonstrate the basic properties second.
	We also outline improvements and tasks required to realize an application using the SADS primitive.

@@

	A verifiable computation (VC) is one in which computation can be performed on behalf of a requester, or client, by an untrusted resource but can be verified to be correct by the client.
	In this scenario, the client usually cannot, or wishes not to, perform the entire computation themselves and thus needs a way to verify the computation efficiently. 
	The growth of outsourced computation in the form of cloud computing has attracted a strong interest in the VC problem, and a considerable amount of research has been devoted to these problems \cite{evsc}.

	The Streaming Authenticated Data Structure scheme (SADS) does not require any interaction between the client and the server while the stream is observed.
	Three important properties are obtained using this scheme :
	\begin{enumerate}[a.]
		\item Independence of prover (server) and verifier(client) : the prover and the verifier update their internal state without interaction.
		\item Efficiency : It can be shown that an exponential improvement for many commonly queries in the prover's running time can be achieved.
		\item Expressiveness : a wide range of queries such as membership/ non-membership, successor, range search and frequencies can be supported using this scheme.
	\end{enumerate} 
	The ultimate goal of the proposed scheme is to implement the SADS scheme that enable the verification of computation performed by an untrusted resource.
